Simple Type Theory is not too Simple

### 2021-03-29 article.tex
Update bibliography

In the same time, some proof assistants have made impressive progress on the algebra front. Indeed, in 2003 Laurent Chicli, as the topic of his PhD thesis, formalized sheaves and affine schemes in the proof assistant Coq based on a powerful dependent type theory known as the \emph{Calculus of Inductive Constructions} \cite{chiclithesis}. More recently, in 2019 Grothendieck's schemes have been formalized by a group of mainly six mathematicians led by Kevin Buzzard using the brave new Lean theorem prover also based on a dependent type theory\footnote{\url{https://github.com/ramonfmir/lean-scheme}} \cite{schemesinLean}. \\

@@

>>>>

In the same time, some proof assistants have made impressive progress on the algebra front. Indeed, in 2003 Laurent Chicli, as the topic of his PhD thesis, formalized sheaves and affine schemes in the proof assistant Coq based on a powerful dependent type theory known as the \emph{Calculus of Inductive Constructions} \cite{chiclithesis}. More recently, in 2019 Grothendieck's schemes \cite{GrothendieckEGAI} have been formalized by a group of mainly six mathematicians led by Kevin Buzzard using the brave new Lean theorem prover also based on a dependent type theory\footnote{\url{https://github.com/ramonfmir/lean-scheme}} \cite{schemesinLean}. \\

@@

	\bibitem{GrothendieckEGAI}
	Grothendieck A.:
	\newblock \textit{\'El\'ements de g\'eom\'etrie alg\'ebrique. I. Le langage des sch\'emas}.
	\newblock Inst. Hautes \'Etudes Sci. Publ. Math., no. 4, 228. MR 217083 (1960)
